What is happening on Twitter? Tweet analysis and undergraduate research projects

### 2020-05-26 Rmd/jse-special-issue-2020.Rmd
updated ms
removed material on best practices for reproducibility

1. Student experience with data analysis software
1. Student research interests and goals
1. Best practices for reproducibility

@@

### Best practices for reproducibility

@@

@@

We used functions from the `rtweet` R package to parse tweet JSON into a data frame. 
We divided JSON arrays into their component vectors and added them
to the data frame.

We then divided tweet text into words with functions from the `tidytext` R package. We discarded commonly used "stop words" 
and emojis.

Latent Dirichlet allocation models require that the corpus be inputted as a 
document by term matrix. Each row corresponds to a single document (a single 
tweet), and each column is a single term (or word). Each cell contains a 
count (the number of 
occurrences of a term in the specified document). We created a document by 
term matrix with the R function `cast_dtm` from the `tidytext` package.

@@

>>>>

1. Student experience with data analysis software
1. Student research interests and goals

@@

@@

Our analyses use three fields from each tweet: date ("created_at"), tweet identifier 
("id_str"), and tweet text ("text"). The "created_at" field is a character string containing 
the date and time of the tweet. Every tweet has a unique identifier, the "id_str" value. The 
"text" field contains the unicode representation of the message. For our topic modeling, a single day defines a single "corpus", and a single tweet 
corresponds to a single "document".

@@

We used functions from the `rtweet` R package to parse tweet JSON into a data frame. 
We then divided tweet text into words with functions from the `tidytext` R package. We 
discarded commonly used "stop words" and emojis.

Latent Dirichlet allocation models require that the corpus be inputted as a 
document by term matrix. In a document by term matrix, each row corresponds to a single document (a single 
tweet), and each column is a single term (or word). Each cell contains a 
count (the number of 
occurrences of a term in the specified document). We created a document by 
term matrix with the R function `cast_dtm` from the `tidytext` package.

@@

## Appendix 3: R analysis code
